---
title: "vbhavya_OriginalHomeworkCode_01"
author: "Bhavya Deepti Vadavalli"
date: "2023-09-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework 1 for AN/BI 588: Push It! - Preliminary

The goal of the homework is to demonstrate our knowledge and understanding of using an intergrated version of RStudio and Github in a collaborative way

For this, we need to follow the following steps: 

1. Create a Github repo called AN588-Week-2-BUlogin (Here's the link to mine! https://github.com/bhavya-dv/AN588-Week-2-vbhavya)
  
  Make your group members and Chris a collaborator on the repo. The group members will share comments about your work and you will do the same. This is an exercise in sharing your work with others. 
  
2. Create a new project on RStudio, and connect the repo from Github to RStudio. We have already done these steps in Module 3, Step 4, Version 1. Link here: https://fuzzyatelin.github.io/bioanth-stats/module-03/module-03.html#Step_4,_version_1_-_Creating_a_new_R_project_by_cloning_a_remote_repository_on_GitHub

3. Make an RMarkdown file with the challenges from Module 3. Push it! and wait for your peers to share their comments. 

##Challenge 1


``` {r challenge1}
#creating a vector with the sentence 
ulysses <- c("Stately",",","plump","Buck","Mulligan","came","from","the","stairhead",",","bearing","a","bowl","of","lather","on","which","a","mirror","and","a","razor","lay","crosed",".") 

#removing all punctuation
ulysses <- gsub("[[:punct:]]","",ulysses) #replaces punctuation with empty string?

library(stringi) #stri_remove_empty(), used below, is in package stringi
ulysses <- as.character(stri_remove_empty(ulysses, na_empty = FALSE)) #removes empty strings from a vector
ulysses #ulysses is now a vector with no punctuation

req_ul <- ulysses[seq(from = 1, to = 22, by = 3)] #the required set of every third string

req_ul
```


